N-dimensional Tic Tac Toe, and Adventure in Modules

### 2017-05-12 paper/paper.tex
added n-dimensionality discussion, could use some word smithing

  \section{Introduction}

@@

	\section{Design Decisions}
  % (Most important!) Describe in detail 3-5 design decisions you made during your
  % project, with respect to abstraction and/or modularity. For example, what is a
  % piece of information that you chose to hide and why? How did you decide on a
  % particular way of separating your system into modules compared to another. How
  % did you reduce coupling between two modules? These design decisions should
  % emphasize how you applied ideas from the papers we’ve read (and associated
  % discussions) to the design of your project. It might be helpful here to
  % include snippets from old versions (or hypothetical alternative versions) of
  % your project to compare and contrast with the final version.
  \subsection{Creating an Abstract Game Engine}
  \subsection{Higher Ordered Signatures, and the ``Include'' incantation}
  \subsection{Separation of IO, or How I learned to not fight SML in search of Purity}
  In the first implementation of our project we simulated Haskell's IO monad by
  creating a ``show'' signature, and an ``IO'' functor, as shown below:

@@

  \subsection{You can do it in 2-dimensions, but can you do it in n-dimensions!}
  \subsection{The Functor is love, the Functor is life}

>>>>

@@

	\section{Design Decisions}
  % (Most important!) Describe in detail 3-5 design decisions you made during your
  % project, with respect to abstraction and/or modularity. For example, what is a
  % piece of information that you chose to hide and why? How did you decide on a
  % particular way of separating your system into modules compared to another. How
  % did you reduce coupling between two modules? These design decisions should
  % emphasize how you applied ideas from the papers we’ve read (and associated
  % discussions) to the design of your project. It might be helpful here to
  % include snippets from old versions (or hypothetical alternative versions) of
  % your project to compare and contrast with the final version.
  \subsection{Creating an Abstract Game Engine}
  % How we came up with the abstract design
  \subsection{Higher Ordered Signatures, and the ``Include'' incantation}
  % Something about how previously we just had signature -> structure -> functors
  % but with include it became possible to 
  \subsection{Separation of IO, or How I learned to not fight SML in search of Purity}
  In the first implementation of our project we simulated Haskell's IO monad by
  creating a ``show'' signature, and an ``IO'' functor, as shown below:

@@

  \subsection{You can do it in 2-dimensions, but can you do it in n-dimensions!}
  Initially, we had conceived on implementing a pokemon battle simulator. As we
  dove into the problem domain we realized that instead of falling into a
  specific, flow-chart design with modules like: Pokemon, Combat, Moves etc. it
  would be better design to create an abstract game engine and then make pokemon
  \textit{an instance of} the abstract game engine. A similar pattern occurred
  during our first implementation of the matrix library utilized by the tic tac
  toe state viz. we realized we wrote a, too specific, flowchart-y instance of a
  matrix library. Thus, in the spirit of modularity, we refactored the matrix
  library to implement an abstract \texttt{CONTAINER} signature. Then based on
  this signature, it became possible to create sub-signatures that specified the
  types of the CONTAINER signature. A good example is shown below:

  \begin{verbatim}
    signature CONTAINER = sig

      (* ADT of the container *)
      type 'a container
      (* type used to index the container *)
      type index
      (* type used to represent the size of the container *)
      type size
    ...
    end

    (* Matrices that are square and so only need size to be a single int *)
    signature SQUAREMATRIX = sig

      include CONTAINER where type size = int

      val intToIndex : 'a container * int -> index

    end

  \end{verbatim}
  In this example we show the relevant parts of the \texttt{CONTAINER} signature
  and how we used that signature to create a \textit{more specific}
  \texttt{SQUAREMATRIX} signature e.g. a matrix whose size datatype need only be
  a single integer value. This allows for a very flexible and modular
  implementation, in addition to square matrices we could create jagged matrices
  by following the same pattern viz. defining a \texttt{JAGGEDMATRIX} and
  setting size to ``int * int''.

  Not only is the second layer of abstraction useful for changing matrix
  properties on the fly, but it is also useful for changing the underlying
  implementation and dimensionality of the matrix. With this design we were able
  to create a functor that, when given a structure of type
  \texttt{SQUAREMATRIX}, and a structure of type \texttt{VECT} will return a
  matrix of whose underlying datatype is implemented by a structure, V of type
  \texttt{VECT}, that dictates the underlying datatype of the matrix, and a
  structure M, of type \texttt{SQUAREMATRIX} that specifies the datatype that
  stores the V structure. For example, we create matrices that are created with
  arrays, vectors and lists by passing each as a structure of type
  \texttt{VECT}; any such data structure is viable as long as it supports the
  \texttt{VECT} signature. By altering the structure M, of type
  \texttt{SQUAREMATRIX} we create n-dimensional matrices. So by varying both we
  gain the ability to create n-dimensional matrices, with abstracted underlying
  data types. Thus, the double abstracted design of our matrix library is a
  semantic definition of a matrix, which separates and abstracts the underlying
  datatype implementation from the dimensionality of the matrix and the
  underlying implementation details, thereby allowing for extreme reuse and
  flexibility.

  \subsection{The Functor is love, the Functor is life}
  % How functors enabled our clean decomposition and modular design
